Discrete Quantum Theories and Computing

### 2018-11-29 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Added a TODO...

\begin{definition}[Pullback of Observables]\label{def:observable2random-variable}Consider
an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
If we restrict $\varphi$ on the classical event space~$2^{\Omega}$
and consider $\varphi:2^{\Omega}\rightarrow\events$, then the pullback
of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$
defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.\end{definition}

>>>>

\begin{definition}[Pullback of Observables]\label{def:observable2random-variable}Consider
an observable~$\mathbf{O}$ diagonalizable by an orthonormal basis
$\Omega=\left\{ \ket{0},\ket{1},\ldots,\ket{D-1}\right\} $ so that
$\mathbf{O}$ has spectral decomposition $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\proj{i}$.
If we restrict $\varphi$ on the classical event space~$2^{\Omega}$
and consider $\varphi:2^{\Omega}\rightarrow\events$, then the pullback
of $\mathbf{O}$ by $\varphi$ is a random variable $\varphi^{*}\mathbf{O}:\Omega\rightarrow\mathbb{R}$
defined by $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\left\{ \ket{i}\right\} }$.
\todo{Put the definition of indicator function!}\end{definition}
